### 2015-02-09 paper_40_mpi.tex
adding a variable for scaling

            As long as those 5 features are met, the range can be anything.  The range of $[-100,100]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-1,1]$.  It maybe makes sense to use variables for the range.  The formulas are designed to fall in the range $[-100,100]$.  Thus scaling can be applied to obtain values in any appropriate range.

>>>>

    As long as those 5 features are met, the range can be anything.  
    The range of $[-1,1]$ was chosen because it is easy to scale 
    to a different range such as $[-10,10]$ or $[-100,100]$.  
    It maybe makes sense to use variables for the range.  
    The formulas are designed to fall in the range $[-100,100]$.  
    Thus scaling can be applied to obtain values in any appropriate range. 
    The scaling is denoted with the variable $k$.  The scale will be the same
    for all 5 elements.
